Paper_analyses

### 2022-03-03 Paper_Analyses_subj_obje_arousal.Rmd
tracking latests changes
forgot to track these for a bit

View(var.data)
# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)

@@

 # same thing as above with variance
# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
  ggplot(aes(`percentage of variance`))+
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+

@@

@@

@@

colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
colnames(resamp_1st_reshuf)
# create emoty  storage rame for eigenvakues
eigen_first_reshuf<- as.data.frame(eugentest)
eigen_first_reshuf[,]<- NA

@@

# create empty storage for correlations
cor_first_reshuf<- as.data.frame(cortest)
cor_first_reshuf[,]<- NA
# cor_first_reshuf<- as.data.frame(cor_first_reshuf)

@@

for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))

resampled_temp_reshuf<-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = F),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = F),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = F),
            arousal = sample(arousal, replace = F),
            valence = sample(valence, replace = F))

@@

# agg by pp

```{r}
clustering_new_pre_PCA3.1.scale_agg_bysid<- clustering_new_pre_PCA3.1%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3.1.scale_aft_agg_bysid<- clustering_new_pre_PCA3.1.scale_agg_bysid%>%
  mutate_if(is.numeric, scale)

res.mfa_agg_bysubj <- FactoMineR::MFA(clustering_new_pre_PCA3.1.scale_agg_bysid, 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

boostrap subjct results

factoextra::fviz_eig(res.mfa_agg_bysubj)
factoextra::fviz_mfa_group(res.mfa_agg_bysubj)

res.mfa_bio_vs_self2_k2$eig
res.mfa_agg_bysubj$eig
res.mfa_agg_bysubj$quanti.var$cor
res.mfa_agg_bysubj$group$cos2

```{r}
colnames(resampled_temp_bysubj)
resamp_1st_bysubj<- data.frame(matrix(NA, nrow = 1, ncol = 8))

# cnames_resamp_subj<- names(resampled_temp_bysubj)
colnames(resamp_1st_bysubj)<- cnames_resamp_subj
colnames(resamp_1st_bysubj)
# create emoty  storage rame for eigenvakues
eigen_first_bysubj<- as.data.frame(eugentest)
eigen_first_bysubj[,]<- NA

# create empty storage for correlations
cor_first_bysubj<- as.data.frame(cortest)
cor_first_bysubj[,]<- NA
# cor_first<- as.data.frame(cor_first)

# res.mfa_bio_vs_self2_k2$group$correlation
partials_first_bysubj <- as.data.frame(res.mfa_bio_vs_self2_k2[["partial.axes"]][["contrib"]])
partials_first_bysubj[,]<- NA
partials_first_bysubj
partials_first_bysubj$sim_no<- NA

# hierarquical clustering
clustering_new_pre_PCA3.1.scale_agg_bysid$ssid<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$ssid)
# clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription<- as.character(clustering_new_pre_PCA3.1.scale_agg_bysid$stimDescription)

groups_first_bysubj<-as.data.frame(  res.mfa_bio_vs_self2_k2$group$correlation)
# res.mfa_bio_vs_self2_k2$group$correlation

groups_first_bysubj[,]<- NA
groups_first_bysubj
groups_first_bysubj$sim_no<- NA

#################be careful to use the correct mfa.res_res. a few times i forgot to use the right one and got constants in the updated dataframes (e.g. partials)
colnames(clustering_new_pre_PCA3.1.scale_agg_bysid)

for (i in 1:1000) {
  message(sprintf("$$$$$RUNING sim %i", i))

  resampled_temp_bysubj<- fabricatr::resample_data(clustering_new_pre_PCA3.1.scale_agg_bysid, 
                                  N = c(51),
                                  ID_labels = c("ssid"),
                                  unique_labels = TRUE)
  # View(resampled_temp_bysubj)
  resampled_temp_bysubj$sim_no = i
  # resampled_temp_bysubj$ssid_new <- as.factor(substr(resampled_temp_bysubj$stimDescription_unique,1,6))
  # resampled_temp_bysubj$newstim <- substr(resampled_temp_bysubj$stimDescription_unique,7,30)
  # resampled_temp_bysubj$stimDescription<- as.factor(resampled_temp_bysubj$stimDescription)

# run PCA on the resampled data
  # colnames(resampled_temp_bysubj)
    message(sprintf("$$$$$fitting PCA %i", i))
    mfa.res_bysubj <- FactoMineR::MFA(resampled_temp_bysubj[,1:6], 
               group = c(1, 3, 2), 
               type = c("n", "s", "s"),
              # ind.sup = c(1),
              ncp = 2,
               name.group = c("sid","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = FALSE)

# store the eigen values
message(sprintf("$$$$$storing PCA %i", i))
eugentest_bysubj<- as.data.frame(mfa.res_bysubj$eig[1:2,])
eugentest_bysubj$sim_no<- i

cortest_bysubj<- as.data.frame(mfa.res_bysubj$quanti.var$cor)
cortest_bysubj$sim_no = i

partials_temp_bysubj<- as.data.frame(mfa.res_bysubj$partial.axes$cor)
partials_temp_bysubj$sim_no = i

# groups
group_temp_bysubj<- as.data.frame(mfa.res_bysubj$group$cos2)
group_temp_bysubj$sim_no = i

# update the initial d=frames
  message(sprintf("$$$$$upating dataframes %i", i))
  resamp_1st_bysubj<- (bind_rows(resamp_1st_bysubj, resampled_temp_bysubj))
eigen_first_bysubj<- bind_rows(eigen_first_bysubj, eugentest_bysubj)
cor_first_bysubj<- bind_rows(cor_first_bysubj, cortest_bysubj)
partials_first_bysubj<- bind_rows(partials_first_bysubj, partials_temp_bysubj)
groups_first_bysubj<- bind_rows(groups_first_bysubj, group_temp_bysubj)
  message(sprintf("$$$$$completed iteration%i", i))
}

resamp_1st_bysubj
View(resamp_1st_bysubj)

resamp_1st_bysubj

resamp_1st_bysubj%>%
  subset(sim_no == 11)

visualise boostrap CIs for agg by subjec

```{r}
eigen_first_bysubj%>%
  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 1" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
  # facet_grid(~component)+
    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_agg_bysubj$eig[1],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = 1, linetype = "dashed")
  # ggtitle("distribution of boostraped eigen values for component  1 
          # red dot = observed eigenvalue, boostrapped 95%CI")+
  # annotate("text", x = 1.2, y = 20, label = "prob of obs eigen>= boot eigen = 51%")

eigen_first_bysubj%>%
  mutate(component =as.factor(substr(rownames(eigen_first_bysubj), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue) & component == "comp 2" )%>% #select only component 1 and remove nas I introduced in the dataframe
  mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE)) %>% #create 95% to descrive interval around the observed estimate
  # mutate(probabcheck= sum(eigenvalue>=res.mfa_bio_vs_self2_k2$eig[1])/n())
  ggplot(aes(eigenvalue))+
  geom_histogram(alpha = .2)+
    geom_density()+
  # facet_grid(~component)+
    geom_errorbar(aes(xmin = min(perc_5), xmax=max(perc_95), y = 10), color = "gray30")+
  geom_point(x = res.mfa_agg_bysubj$eig[2],y = 10,size = 2, color = "red")+

  theme_classic()+
  geom_vline(xintercept = 1, linetype = "dashed")

variables and dimension corelations
```{r}
cor_first_bysubj %>%
  mutate(variable = as.factor(substr(rownames(cor_first_bysubj), 1,6)))%>%
    subset(!is.na(Dim.1)) %>%
  # create interval per variable
  group_by(variable)%>%
   mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
         perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  # subset(variable == "arousa"|variable == "valenc")%>%
  # select(c("arousal", "valence"))%>%
  ggplot(aes(Dim.1)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =.6 ), color = "gray30")+
  facet_grid(~variable)+
  # geom_point(xlim = res.mfa_agg_bysubj$quanti.var$cor, y = 4, color = "red", size = 2)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  #  geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

```
Agg within participant by neg pos etc (using normative data)
With and without selfreports

```{r}
?cut
#create valence categories based ion self reports (IAPS validation)
clustering_new_pre_PCA3_val_vat<- clustering_new_pre_PCA3%>%
  mutate(valence_iaps_cat = cut(ValenceMean,3, labels = c("neg", "mid", "pos")))

# scale within subject
# aggregate by subject and

View(clustering_new_pre_PCA3_val_vat)
# clustering_new_pre_PCA3_val_vat%>%
#   group_by(ssid)%>%
#   mutate_if(is.numeric, scale)

clustering_new_pre_PCA3_val_vat_agg<- clustering_new_pre_PCA3_val_vat%>%
  group_by(ssid, valence_iaps_cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

library(factoextra)
library(FactoMineR)

colnames(clustering_new_pre_PCA3_val_vat_agg)
clustering_new_pre_PCA3_val_vat_agg[,c(2,5,6,7,8,9)]

FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)], 
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               # "s", "s", "s"
               name.group = c("ss_id_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

# scale
clustering_new_pre_PCA3_val_vat_agg_scale<- clustering_new_pre_PCA3_val_vat_agg[,c(1,2,5,6,7,8,9)]

clustering_new_pre_PCA3_val_vat_agg_scale%>%
   # group_by(ssid)%>%
  mutate_if(is.numeric, scale)

clustering_new_pre_PCA3_val_vat_scale_then_agg<- clustering_new_pre_PCA3_val_vat%>%
  group_by(ssid)%>%
  mutate_if(is.numeric, scale)%>%
  group_by(ssid, valence_iaps_cat)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

clustering_new_pre_PCA3_val_vat_scale_then_agg1<- clustering_new_pre_PCA3_val_vat_scale_then_agg[,c(1:2, 5:9)]

?FactoMineR::MFA
res.mfa_val_cat_scal<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               name.group = c("ss_id_stim","auton","subj"),
               num.group.sup = c(1),
               # ind.sup = c(1,2),
               graph = TRUE)

?FactoMineR::MFA
View(res.mfa_val_cat_scal)

# force k = 2

res.mfa_val_cat_scal_k2<- FactoMineR::MFA(clustering_new_pre_PCA3_val_vat_scale_then_agg1,
               group = c(2, 3, 2), 
               type = c("n", "s", "s"),
               name.group = c("ss_id_stim","auton","subj"),
               num.group.sup = c(1),
               ncp = 2,
               # ind.sup = c(1,2),
               graph = TRUE)

res.mfa_val_cat_scal_k2$eig

fviz_mfa_ind(res.mfa_val_cat_scal, 
             habillage = "valence_iaps_cat", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, 
             ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

# we can sorta see that while things allign relativelly well on sujective dimension, they don't allugn very well on the autonomic dimension

save.image("subjobjPCAfeb9.RData")
```

>>>>

View(var.data)
# inferential PCA
var.PCA.scr_hr_pup <-InPosition::epPCA.inference.battery(var.data, 
                                       scale = TRUE, 
                                       center = TRUE, 
                                       # DESIGN = var.design_asd, 
                                       # make_design_nominal = TRUE, 
                                       graphs = TRUE, k = 0, 
                                       test.iters = 1000, 
                                       constrained = FALSE, 
                                       critical.value = 2)
InPosition::epCA.inference.battery()

@@

 # same thing as above with variance
# quantile(eigen_first$`percentage of variance`,.95, na.rm = TRUE)
eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
  subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE)) %>%
  ggplot(aes(`percentage of variance`))+
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y = .3), color = "gray30")+
  geom_point(x = res.mfa_bio_vs_self2_k2$eig[1,2],y = .3,size = 3, color = "red")+

@@

eigen_first%>%
  mutate(component =as.factor(substr(rownames(eigen_first), 1,6)))%>%
    group_by(component)%>%
  # subset(!is.na(`percentage of variance`) & component == "comp 1" )%>%
  mutate(perc_5 = quantile(`percentage of variance`,.025, na.rm = TRUE),
         perc_95 = quantile(`percentage of variance`,.975, na.rm = TRUE))%>%
  group_by(component)%>%
  summarise_if(is.numeric, mean)

@@

  groups_first

  res.MFA_stim_val_scale$group$contrib
  res.MFA_stim_val_scale[["ind"]][["coord"]])

@@

colnames(resamp_1st_reshuf)<- cnames_resamp_reshufl
colnames(resamp_1st_reshuf)

# create emoty  storage rame for eigenvakues
eigen_first_reshuf<- as.data.frame(res.mfa_bio_vs_self2_k2$eig)
eigen_first_reshuf[,]<- NA

@@

# create empty storage for correlations
cor_first_reshuf<- as.data.frame(cor_first_reshuf)
cor_first_reshuf[,]<- NA
# cor_first_reshuf<- as.data.frame(cor_first_reshuf)

@@

for (i in 1:10000) {
  message(sprintf("$$$$$RUNING sim %i", i))

# changed below to replace treue - shuflle with replacement
  # https://stats.stackexchange.com/questions/104040/resampling-simulation-methods-monte-carlo-bootstrapping-jackknifing-cross?rq=1
  # See the question on permutation vs bootstrapping - "The permutation test is best for testing hypotheses and bootstrapping is best for estimating confidence intervals".
resampled_temp_reshuf <-    clustering_new_pre_PCA3.1_copy[,c(1,2,3, 5:9)] %>%
  group_by(ssid)%>%
  transform(pup_basCor = 
              sample(pup_basCor, replace = FALSE),
            Bio_Mean_HR_dif = sample(Bio_Mean_HR_dif, replace = FALSE),
            log_BIO_CDA.PhasicMax = sample(log_BIO_CDA.PhasicMax, replace = FALSE),
            arousal = sample(arousal, replace = FALSE),
            valence = sample(valence, replace = FALSE))

@@

save(clustering_new_pre_PCA3.1_copy,resampled_temp_reshuf,
     resamp_1st_reshuf,
     eigen_first_reshuf,
     cor_first_reshuf,
     res.mfa_bio_vs_self2_k2,
     clustering_new_pre_PCA3.1, file = "resample_hierar.RData")

visualise resshufled null data

eigen_first_reshuf%>%
  mutate(component =as.factor(substr(rownames(eigen_first_reshuf), 1,6)))%>% #retrieve names for components
  subset(!is.na(eigenvalue))%>% #select only component 1 and remove nas I introduced in the dataframe
  group_by(component)%>%

   mutate(perc_5 = quantile(eigenvalue,.025, na.rm = TRUE), 
         perc_95 = quantile(eigenvalue,.975, na.rm = TRUE))%>%
  ungroup()%>%
    group_by(component)%>%
  mutate(eig_obs_dim = if_else(component == "comp 1", 
                               res.mfa_bio_vs_self2_k2$eig[1],
                               res.mfa_bio_vs_self2_k2$eig[2])) %>% #store observed to visualise ion the null
  mutate(prob = paste(((sum(eigenvalue>=eig_obs_dim))/n())*100, paste0("%"))) %>%
  ggplot(aes(eigenvalue))+
  geom_histogram(aes(y=..density..),bins = 500, alpha = .3) +  # scale histogram y
  geom_density(col = "red", alpha = .001)+
  # facet_grid(~component)+
    geom_vline(aes(xintercept = eig_obs_dim),size = 2, color = "red", linetype = "dashed", alpha = .3)+
  geom_point(aes(x = eig_obs_dim, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+

  theme_classic()+

  # annotate(aes(text, label = prob))

  theme_classic()+
  facet_grid(~component)

# component 1 is significant
```

cor reshudl

cor.test_obsmfa<- as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor) %>%
   mutate(variable = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$quanti.var$cor)), 1,6)))%>%
 gather(dimension, value_dimenion, -variable)

cor.test_obsmfa

colnames(cor_first_reshuf)
cor_first_reshuf1<- cor_first_reshuf %>%
  mutate(variable = as.factor(substr(rownames(cor_first_reshuf), 1,6)))%>%
    gather(dimension, value_dimenion, -variable, -sim_no) %>%

  group_by(variable,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
  subset(!is.na(value_dimenion))

# this mighgt have to do with the wrong test
left_join(cor_first_reshuf1, cor.test_obsmfa, by = c("variable", "dimension")) %>%
  group_by(variable,dimension)%>%
     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
  # the line above computes the probability that the correlation is more extreme (in magnitutde) thn the observed one

  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  # geom_point(aes(x = value_dimenion.y, y = -2))+
    # geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+
  facet_grid(variable~dimension)+
   geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+

  theme_classic()

```{r}
partials_first_1_obs<- as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor) %>%
   mutate(dimension_partial = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 1,4)),
           group = as.factor(substr(rownames(as.data.frame(res.mfa_bio_vs_self2_k2$partial.axes$cor)), 5,9)))%>%
 gather(dimension, value_dimenion,-group,-dimension_partial)

partials_first_reshuf_1<- partials_first_reshuf %>%
  mutate(dimension_partial = as.factor(substr(rownames(partials_first_reshuf), 1,4)),
         group = as.factor(substr(rownames(partials_first_reshuf), 5,9)))%>%
   gather(dimension, value_dimenion, -group, -sim_no, -dimension_partial) %>%
   group_by(dimension_partial,dimension,group)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))%>%
  subset(!is.na(value_dimenion))

left_join(partials_first_reshuf_1,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
  group_by(dimension_partial,dimension, group)%>%
   # group_by(variable,dimension)%>%
     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
  subset(dimension_partial == "Dim1")%>%
   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
  facet_grid(dimension~group)+

  theme_classic()+
  ggtitle("partial to dimension 1")

left_join(partials_first_reshuf_1,partials_first_1_obs,by = c("dimension_partial", "group", "dimension")) %>%
  group_by(dimension_partial,dimension, group)%>%
   # group_by(variable,dimension)%>%
     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%
  subset(dimension_partial == "Dim2")%>%
   # mutate(perc_5 = quantile(Dim.1,.025, na.rm = TRUE),
   #       perc_95 = quantile(Dim.1,.975, na.rm = TRUE))%>%
  ggplot(aes(value_dimenion.x)) +
  geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +
  geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-5 ), color = "gray30")+
  geom_vline(aes(xintercept = value_dimenion.y),size = 2, color = "red", linetype = "dashed", alpha = .3)+
  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
  facet_grid(dimension~group)+

  theme_classic()+
  ggtitle("partial to dimension 2")

Groups

groups_first_1boot<- groups_first%>%
  mutate(group = as.factor(substr(rownames(groups_first), 1,4)))%>%
  gather(dimension, value_dimenion,-group,-sim_no)%>%
  # -perc_5,-perc_95, 
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion,.975, na.rm = TRUE))

?boot::boot.ci
boot::boot.ci(groups_first_1boot$value_dimenion, type = "bca")[1]
?bootBCa
bootBCa(.5, groups_first_1boot$value_dimenion, n = 2600)[1]
left_join(groups_first_1boot, groups_first_obs,by = c("group", "dimension"))%>%

  ggplot(aes(value_dimenion)) +
   geom_histogram(aes(y=..density..), alpha=0.5,
                 position="identity")+
  geom_density(alpha=.2) +

   geom_errorbarh(aes(xmax = perc_95, xmin = perc_5, y =-3 ), color = "gray30")+
   geom_point(aes(x = value_dimenion_obs, y = -3))+
    geom_vline(xintercept = 0, color = "red", linetype = "dashed", alpha = .3, size = 1)+

  facet_grid(dimension~group)+
  # geom_vline(xintercept = .5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
   # geom_vline(xintercept = -.5, color = "red", linetype = "dashed", alpha = .1, size = 1)+
  theme_classic()

groups_first_reshuf<- groups_first_reshuf%>%
  mutate(group = as.factor(substr(rownames(groups_first_reshuf), 1,4)))

group_cordf<- as.data.frame(res.mfa_bio_vs_self2_k2$group$correlation)
group_cordf$group<-as.factor(substr(rownames(group_cordf), 1,4))

group_cordf1<- group_cordf%>%
gather(dimension, value_dimenion, - group)

groups_first_reshuf1<- left_join(groups_first_reshuf, group_cordf1)

# View(groups_first_reshuf)
groups_first_reshuf1<- groups_first_reshuf %>%
  gather(dimension, value_dimenion, -group, -sim_no) %>%
  subset(!is.na(value_dimenion))

 left_join(groups_first_reshuf1, group_cordf1, c("group", "dimension"))%>%
   group_by(group,dimension)%>%
   mutate(perc_5 = quantile(value_dimenion.x,.025, na.rm = TRUE),
         perc_95 = quantile(value_dimenion.x,.975, na.rm = TRUE))%>%
     mutate(prob1 = paste(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y)))/n())*100, paste0("%")))%>%
   mutate(prob = if_else(((sum(abs(value_dimenion.x)>=abs(value_dimenion.y))/n())*100)<5, "p < .05", "ns")) %>%

  ggplot(aes(value_dimenion.x)) +
  geom_histogram(bins = 500)+

  geom_density(alpha=.2) +
  facet_grid(dimension~group)+
     geom_vline(aes(xintercept = value_dimenion.y), linetype = "dashed", color = "red")+
   # geom_vline(aes(xintercept = Dim.2.y),  linetype = "dashed", color = "blue")+
  geom_point(aes(x = value_dimenion.y, y = 1, shape = prob),size = 3,  color = "red", alpha = .5)+
  # geom_histogram(aes(y=..density..), alpha=0.5,
  #                position="identity")+

  theme_classic()

res.mfa_bio_vs_self2_k2$group$correlation
